
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Tahseen Robbani} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{tarobbani@gmail.com}
\moveleft.5\hoffset\centerline{256-479-5800}
\moveleft.5\hoffset\centerline{\url{http://tahzabbani.xyz}}
\moveleft.5\hoffset\centerline{\url{https://github.com/tahzabbani}}

%----------------------------------------------------------------------------------------

\begin{resume}


\section{EDUCATION}

University of Alabama at Birmingham - Birmingham, AL, expected May 2021 \\
Concentration: Computer Science \\
Minor: Mathematics \\
GPA: 3.95
 

\section{SKILLS} 

{\sl Programming Languages:} 
Java, Javascript, C++, Python, SQL \\
{\sl Markup Languages:} 
HTML, CSS, Markdown, Latex \\
{\sl Frameworks:} JQuery, Bootstrap
 
\section{EXPERIENCE}

{\sl Computer Analyst III} \hfill Summer 2021 - Present \\
Aviation and Missile Solutions, Huntsville, AL 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Updated/implemented parts of radar software in C++.
\item Continuously learned more about Linux commands and their uses in streamlining tasks.
\item Traveled to three locations across the country to collect data during test events. 
\end{itemize} 

{\sl IT Intern} \hfill Summer 2019 - Present \\
Therapy Brands, Birmingham, AL 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Helped in projects such as employee organization within our Jumpcloud, Zoom setup, and Slack improvements.
\item Helped employees with their general technology problems through Zendesk tickets.
\item Created automated tasks using Microsoft Flow and Zapier for e-prescriptions.
\end{itemize} 

{\sl Web Developer Intern} \hfill Summer 2020 \\
Kinetic Communications, Birmingham, AL
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed my own portfolio website using HTML, CSS, Javascript, Bootstrap, and JQuery while receiving feedback from the developers at Kinetic. 
\item Helped maintain websites that Kinetic created by editing their contents via WordPress. 
\end{itemize}

\section{COMMUNITY \\ SERVICE}

{\sl Foster Parent for Kittens} \hfill 2018 - 2021 \\
Greater Birmingham Humane Society, Birmingham, AL
\begin{itemize}
\item House kittens who are underweight for being neutered or have disabilities. The foster period is usually around one month.
\end{itemize}


\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

{\sl Taste of India Liaison} \hfill Winters 2019 \& 2020 \\
Asian American Organization at UAB, Birmingham, AL
\begin{itemize}
\item Acted as a leader and guide to liaison dance teams that come to UAB to compete for a weekend.
\end{itemize}

\section{PROJECTS}

{\sl Wedding Website} - Website built from scratch with Python Flask. \\
{\sl Discord Bot} - Bot that uses BeautifulSoup4 to scrape League of Legends data.


%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
