
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Tahseen Robbani} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{tar0025@uab.edu}
\moveleft.5\hoffset\centerline{256.479.5800}
\moveleft.5\hoffset\centerline{\url{http://tahzabbani.xyz}}
\moveleft.5\hoffset\centerline{\url{https://github.com/tahzabbani}}

%----------------------------------------------------------------------------------------

\begin{resume}

 
\section{OBJECTIVE}  

A position in the field of software development after graduating in May 2021 with a special interest in web development and Python. 


\section{EDUCATION}

University of Alabama at Birmingham - Birmingham, AL, expected May 2021 \\
Concentration: Computer Science \\
Minor: Mathematics \\
GPA: 3.95
 

\section{SKILLS} 

{\sl Programming Languages:} 
Java, Javascript, C, Python \\
{\sl Markup Languages:} 
HTML, CSS, Markdown, Latex \\
{\sl Frameworks:} JQuery, Bootstrap \\ 
{\sl Libraries:} BeautifulSoup4 \\ 
{\sl Soft:} Adaptability, Willingness to Learn, Critical Thinking 
 
\section{EXPERIENCE}

{\sl IT Intern} \hfill Summer 2019 - Present \\
Therapy Brands, Birmingham, AL 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] Helped in projects such as Jumpcloud account organization, AWS workstation organization, Zoom setup, and Slack improvements.
\item[-] Helped employees with their general technology problems through Zendesk tickets.
\item[-] Created automated tasks using Microsoft Flow.
\item[-] Managed and maintained over 400 workstations through Solarwinds RMM.
\end{itemize} 

{\sl Web Developer Intern} \hfill Summer 2020 \\
Kinetic Communications, Birmingham, AL
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] Developed my own portfolio website using HTML, CSS, Javascript, Bootstrap, and JQuery while receiving feedback from the developers at Kinetic. 
\item[-] Helped maintain websites that Kinetic created by editing their contents via WordPress. 
\end{itemize}

{\sl Student Fundraiser} \hfill June 2019 \\
UAB Phonathon, Birmingham, AL
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] Made calls to UAB alumni to update contact information, asked how they are doing after school, and asked for funding towards UAB.
\end{itemize}

{\sl Grader} \hfill June 2016 - August 2017 \\
Kumon Math and Reading Center, Madison, AL
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] Graded the math workbooks of students K-9 enrolled in the Kumon learning program.
\item[-] Assisted students with math problems whenever needed.
\item[-] Entered grade data into Kumon's record tracking system.
\end{itemize}

\section{PROJECTS}

Deeper looks into these projects are available on my website linked above.

{\sl Web Scraping Discord Bot}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] placeholder
\end{itemize}

{\sl Personal Portfolio Website}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] placeholder
\end{itemize}

{\sl Block Boy (Flappy Bird Clone)}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] placeholder
\end{itemize}

{\sl Simple Shell Terminal}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[-] placeholder
\end{itemize}

\section{COMMUNITY \\ SERVICE}

{\sl Foster Parent for Kittens} \hfill 2018 - Present \\
Greater Birmingham Humane Society, Birmingham, AL
\begin{itemize} 
\item[-] House kittens who are underweight for being neutered or have disabilities. The foster period is usually around one month.
\end{itemize}


\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

{\sl Taste of India Liaison} \hfill Winters 2019 \& 2020 \\
Asian American Organization at UAB, Birmingham, AL
\begin{itemize}
\item[-] Acted as a leader and guide to liaison dance teams that come to UAB to compete for a weekend.
\end{itemize}

{\sl UAB Association of Computing Machinery Member}
\begin{itemize}
\item[-]
\end{itemize}

\section{RELEVANT \\ COURSEWORK}

CS436 Advanced Algorithms and Applications \\
CS420 Software Engineering \\
CS303 Algorithms and Data Structures \\
CS433 Operating Systems \\
CS330 Computer Organization/Assembly Language \\
CS203 Object-Oriented Programming


%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
